A concise manual to\\\textsc{DEVS Ex Machina}

### 2015-04-23 manual/tex/models.tex

\section{Atomic models}
Atomic models can be made by implementing a sub-class of \textsl{n\_model::AtomicModel}. The most basic functions to be implemented are:
\begin{enumerate}
	\item \textsl{void AtomicModel::extTransition(const std::vector{\textless}n\_network::t\_msgptr{\textgreater} \& inputs)}\\
		Performs the model's external transition. The input argument is a vector with all messages at a certain point in time.
	\item \textsl{void AtomicModel::intTransition()}\\
		Performs the model's internal transition. 
	\item \textsl{t\_timestamp AtomicModel::timeAdvance()}\\
		Should return the model's current time advance value; the amount of time after which the following internal transition occurs. This function should not alter the model in any way.
	\item \textsl{std::vector{\textless}n\_network::t\_msgptr{\textgreater} AtomicModel::output()  const}\\
		Returns the model's output; all messages that are to be send should be returned via this function. This function should not alter the model in any way.
\end{enumerate}

@@

\textbf{Timestamps} that the user has to generate, for example in the \textsl{timeAdvance} function, can be easily constructed using the following constructor: \textsl{t\_timestamp(size\_t)}).\\

@@

When \textbf{sending messages} (\textbf{output function}), there are a few rules you should take into account. The message you want to send can only be a string. This string should be given to the port you want to send it through. The port will then create the actual messages (that are send over the models) and return them to you in a vector. All these messages (from possibly different ports) should be joined in 1 vector and be returned in the output function. The following functions will allow you to do so:
\begin{itemize}
	\item \textsl{t\_portptr Model::getPort(std::string name) const}
	\item \textsl{std::vector{\textless}n\_network::t\_msgptr{\textgreater} Port::createMessages(std::string message)}
\end{itemize} 
Something like this would work: this-{\textgreater}getPort("OUT")-{\textgreater}createMessages(message); \\

@@

\section{Coupled models}
Coupled models only require you to implement them as a sub-class of \textsl{n\_model::CoupledModel}.

\textbf{Adding sub-models} requires following function: \textsl{void CoupledModel::addSubModel(const t\_modelptr\& model)}.

>>>>

\section{Atomic models}
Atomic models can be made by implementing a sub-class of \\ \textsl{n\_model::AtomicModel}. The most basic functions to be implemented are:
\begin{enumerate}
	\item \textsl{void AtomicModel::extTransition(const std::vector{\textless}n\_network::t\_msgptr{\textgreater} \& inputs)}\\
		Performs the model's external transition. The input argument is a vector with all messages at a certain point in time.
	\item \textsl{void AtomicModel::intTransition()}\\
		Performs the model's internal transition. 
	\item \textsl{t\_timestamp AtomicModel::timeAdvance()}\\
		Should return the model's current time advance value; the amount of time after which the following internal transition occurs. This function should not alter the model in any way.
	\item \textsl{std::vector{\textless}n\_network::t\_msgptr{\textgreater} AtomicModel::output()  const}\\
		Returns the model's output; all messages that are to be send should be returned via this function. This function should not alter the model in any way.
\end{enumerate}

@@

\textbf{Timestamps} that the user has to generate, for example in the \textsl{timeAdvance} function, can be easily constructed using the following constructor:\\ \textsl{t\_timestamp(size\_t)}).\\

@@

When \textbf{sending messages} (\textbf{output function}), there are a few rules you should take into account. The message you want to send can only be a string. This string should be given to the port you want to send it through. The port will then create the actual messages (that are send over the models) and return them to you in a vector. All these messages (from possibly different ports) should be joined in 1 vector and be returned in the output function. The following functions will allow you to do so:
\begin{itemize}
	\item \textsl{t\_portptr Model::getPort(std::string name) const}
	\item \textsl{std::vector{\textless}n\_network::t\_msgptr{\textgreater} Port:: \\createMessages(std::string message)}
\end{itemize} 
Something like this would work: this-{\textgreater}getPort("OUT")-{\textgreater} \\createMessages(message); \\

@@

\section{Coupled models}
Coupled models only require you to implement them as a sub-class of \\ \textsl{n\_model::CoupledModel}.

\textbf{Adding sub-models} requires following function: \textsl{void CoupledModel:: \\addSubModel(const t\_modelptr\& model)}.
